---
title: Sample Project
output:
  pdf_document: default
  html_document: default
---
```{r, echo = FALSE, message = FALSE, warning = FALSE, eval = TRUE}
if(!require(tidyverse)) install.packages("tidyverse", repos = "http://cran.us.r-project.org")
if(!require(caret)) install.packages("caret", repos = "http://cran.us.r-project.org")
if(!require(plotly)) install.packages("plotly", repos = "http://cran.us.r-project.org")
library(dslabs)
library(dplyr)
library(caTools)
library(writexl)
library("data.table")
```

# DATASET

## View Data

###Load data from csv file
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
dataset = read.csv('Rx_Regional_Monthly_04_2023.csv')

```

### Structure of dataset
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
str(dataset)
```


### Sample data
```{r, echo = FALSE, message = FALSE, warning = FALSE, eval = TRUE}
head(dataset)
```
### Total rows in dataset
```{r, echo = FALSE, message = FALSE, warning = FALSE, eval = TRUE}
sprintf("%d Rows" ,nrow(dataset))
```


## Data Cleaning

### Check if there are NA's in the data
```{r, echo = FALSE, message = FALSE, warning = FALSE, eval = TRUE}
colSums(is.na(dataset))
```


### Convert the metrics to integer taking care of comma in the value and add the ID's to the categorical dimensions 
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
modifiedDataset <- dataset %>%
  mutate(TRx = as.numeric(gsub(",", "", TRx)),
         EUTRx = as.numeric(gsub(",", "", EUTRx)),
         RRx = as.numeric(gsub(",", "", RRx)),
         NRx = as.integer(gsub(",", "", NRx)) 
         )

colPos <- c(1,2,3,4,5)
modifiedDataset <-  modifiedDataset %>% mutate_at(colPos, funs(factor(.)))

```

### Structure of modified dataset
```{r, echo = FALSE, message = FALSE, warning = FALSE, eval = TRUE}
str(modifiedDataset)
```


### Check any values converted to NA's during char to integer conversion 
```{r, echo = FALSE, message = FALSE, warning = FALSE, eval = TRUE}
colSums(is.na(modifiedDataset))
```
# Data Analysis

## GRID an CHART Analysis

* Since its a large dataset we use boxplot to view the spread of data and used Log to make the data finite and in range

### Data spread State wise TRx

```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
ggplot(data = modifiedDataset,
       mapping = aes(y = TRx, x = `誰..State`)) +
  geom_boxplot() +
  theme(legend.position = "none") +
  ggtitle("Trx by State") +
  scale_y_continuous("TRx (log)", labels = scales::comma) +
  scale_x_discrete("State")  +
  coord_flip()
```

### Channel wise TRx
```{r, echo = FALSE, message = FALSE, warning = FALSE, eval = TRUE}
ggplot(data = modifiedDataset, aes(x = Channel, y = log(TRx), fill = Channel)) +
  geom_boxplot() +
  theme(legend.position = "none") +
  ggtitle("Trx by Channel") +
  scale_y_continuous("TRx", labels = scales::comma) +
  scale_x_discrete("Channel") +
  coord_flip()
```


### Form TLC1 wise TRx
```{r, echo = FALSE, message = FALSE, warning = FALSE, eval = TRUE}
ggplot(data = modifiedDataset, aes(x = `Form..TLC1.`, y = log(TRx), fill = `Form..TLC1.`)) +
  geom_boxplot() +
  theme(legend.position = "none") +
  ggtitle("Trx by Form TLC1") +
  scale_y_continuous("TRx (log)", labels = scales::comma) +
  scale_x_discrete("Form TLC1") +
  coord_flip()
```

### Channel wise Form TLC1 By TRx

```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
ggplot(data = modifiedDataset, aes(x = `Form..TLC1.`, y = log(TRx), fill = `Channel`)) +
  geom_boxplot() +
  theme(legend.position = "bottom") +
  ggtitle("Each Channel spread Form TLC1 By TRx") +
  scale_y_continuous("TRx (log)", labels = scales::comma) +
  scale_x_discrete("Form TLC1") +
  coord_flip()
```



### Top 10 Form TLC1 by Channel based on mean TRx
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
##filter data 
df2 <- 
  modifiedDataset %>% group_by(`Form..TLC1.`,`Channel` ) %>% 
  summarise(MeanTrx = mean(`TRx`)) %>% 
  arrange(desc(MeanTrx)) %>% head(10) 

#plot Most Expensive Building Types by Borough
df2 %>%
  arrange(desc(MeanTrx)) %>% 
ggplot( aes(x = `Form..TLC1.`, y = MeanTrx, fill = `Channel`)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme(legend.position = "bottom") +
  ggtitle("Top 10 Form TLC1 by Channel based on mean TRx") +
  scale_y_continuous("Form TLC1", labels = scales::comma) +
  scale_x_discrete("TRx") 
```


### Create random sample of dataset based on channel
```{r eval= TRUE, echo=TRUE, message=FALSE, warning=FALSE}
dat_small <- modifiedDataset %>% 
  group_by(Channel) %>%
  slice_sample(n=5000)
sprintf("%d sample of Rows grouping by channel" ,nrow(dat_small))

```

### Relation metrics NRx and EUTRx with channel wise
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}

ggplot(data = dat_small, aes(x = log(TRx), y = log(EUTRx), color = `Channel`)) +
  geom_jitter() +
  geom_smooth(method = "lm", colour="black", size=0.5, linetype = "dashed") +
  theme(legend.position = "bottom") +
  facet_wrap(~ Channel) +
  ggtitle("TRx Vs EUTRx Channel Wise") +
  scale_y_continuous("Trx", labels = scales::comma) +
  scale_x_continuous("EUTRx", labels = scales::comma) 

```

# Predective Analysis


### Spliting the data into Training And Test Set in 80-20 ratio
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
#split it into training set
set.seed(3287)
split = sample.split(modifiedDataset$TRx, SplitRatio = 0.8)
training_set = subset(modifiedDataset, split == TRUE)
test_set = subset(modifiedDataset, split == FALSE)
```

```{r, echo = FALSE, message = FALSE, warning = FALSE, eval = TRUE}
sprintf("%d Rows Training Set" ,nrow(training_set))
sprintf("%d Rows Test Set" ,nrow(test_set))
```
## Correlation

### Generating corelated table between the feature
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
library(corrplot)
#calculate correlation
distance_corr <- vapply(training_set, 
                        function(x) { cor(training_set$TRx, as.numeric(x), use = "pairwise.complete.obs") }, 
                        FUN.VALUE = numeric(1))
effect_corr <- vapply(distance_corr, function(x) { ifelse(x >= 0, "Positive", "Negative")}, 
                      FUN.VALUE = character(1))
var_corr <- names(training_set)

# create correlation table
table1 <- data.frame(var_corr, abs(distance_corr), effect_corr)
table1 <- table1[order(-abs(distance_corr)),]
names(table1) <- c("Column/Variable", "Correlation Size", "Correlation Effect")
table1

temp <- training_set[,c(1:9)]    
num <- c(1:9)
temp <- temp %>% mutate_at(num, funs(as.numeric(.)))
#plot table of correlations
corrplot(cor(temp), type = "upper",order = "hclust", 
         tl.col = "black", tl.srt = 45)

corrplot(cor(temp), method="number",number.cex = 0.5)
```

## Multi Regression Modal



### Handeling the items thats present in test set and not present in traning set 
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
#predict Data
data_test_new <- test_set
data_test_new$Specialty[which(!(data_test_new$Specialty %in% unique(training_set$Specialty)))] <- NA
data_test_new$Channel[which(!(data_test_new$Channel %in% unique(training_set$Channel)))] <- NA
data_test_new$誰..State[which(!(data_test_new$誰..State %in% unique(training_set$誰..State)))] <- NA
data_test_new$Form..TLC1.[which(!(data_test_new$Form..TLC1. %in% unique(training_set$Form..TLC1.)))] <- NA
```

### Apply all metrics column in the modal
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
regressor = lm(formula = TRx ~ . ,
               data = training_set)

#Summary of the regression
# summary(regressor)

rSquared<- summary(regressor)$r.squared
standerdError <- summary(regressor)$sigma
sprintf("R Square: %f" ,rSquared)
sprintf("Standerd Error: %f" ,standerdError)


```

### Predict the result
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
y_pred_test = predict(regressor, newdata = data_test_new)


# write_xlsx( data.frame(data_test_new) , "TestData.xlsx")
# write_xlsx( data.frame(y_pred_test) , "predict.xlsx")
```


### Visualising the multi Linear Regression results Channel, TRx and Predicted TRx
```{r, echo = FALSE, message = FALSE, warning = FALSE, eval = TRUE}
ggplot() +
  geom_point(aes(x = data_test_new$Channel, y = data_test_new$TRx) , 
             color="red") +
  geom_line(aes(x= data_test_new$Channel, y = y_pred_test ),
            color="blue") +
  ggtitle('Truth or Bluff (Linear Regression) Predicted Vs Actual') +
  scale_y_continuous("TRX", labels = scales::comma) +
  scale_x_discrete("Channel") +
  xlab('Channel') +
  ylab('TRx')

```

### Visualising the multi Linear Regression results EUTRx, TRx and Predicted TRx
```{r, echo = FALSE, message = FALSE, warning = FALSE, eval = TRUE}
ggplot() +
  geom_point(aes(x = data_test_new$EUTRx, y = data_test_new$TRx) , 
             color="red") +
  geom_line(aes(x= data_test_new$EUTRx, y = y_pred_test ),
            color="blue") +
 ggtitle('Truth or Bluff (Linear Regression) Predicted Vs Actual') +
  scale_y_continuous("TRX", labels = scales::comma) +
  scale_x_discrete("EUTRx", labels = scales::comma) +
  xlab('EUTRx') +
  ylab('TRx')

```


### Apply all correlative NRx,RRx,EUTRx,Channel,Form TLC1 for predecting TRX  
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
regressor = lm(formula = TRx ~ `NRx` + `RRx` + Channel + `Form..TLC1.` ,
               data = training_set)

rSquared<- summary(regressor)$r.squared
standerdError <- summary(regressor)$sigma
sprintf("R Square: %f" ,rSquared)
sprintf("Standerd Error: %f" ,standerdError)


y_pred_test = predict(regressor, newdata =  data_test_new)
```

### Apply all metrics NRx ,RRx for predecting TRX 
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
regressor = lm(formula = TRx ~ `NRx` + `RRx` +`EUTRx` ,
               data = training_set)

#Summary of the regression
summary(regressor)

rSquared<- summary(regressor)$r.squared
sprintf("R Square: %f" ,rSquared)
standerdError <- summary(regressor)$sigma
sprintf("Standerd Error: %f" ,standerdError)

y_pred_test = predict(regressor, newdata = data_test_new )

```

## Random Forest Modal

### Modal with NRx,RRx for predecting TRX with 2 node
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}

library(randomForest)

# now try with 10, 100, 500 tree
regressor=randomForest(TRx ~  `NRx` + `RRx`  , data=training_set, na.action=na.omit,ntree=2)

y_pred =predict(regressor, newdata = test_set )
# write_xlsx( data.frame(y_pred) , "PredDiadata.xlsx")
```

### Visualising the multi Random Forest results Channel, TRx and Predicted TRx
```{r, echo = FALSE, message = FALSE, warning = FALSE, eval = TRUE}
ggplot() +
  geom_point(aes(x = test_set$Channel, y = test_set$TRx) , 
             color="red") +
  geom_line(aes(x= test_set$Channel, y = y_pred ),
            color="blue") +
  ggtitle('Truth or Bluff (Linear Regression) Predicted Vs Actual') +
  scale_y_continuous("TRX", labels = scales::comma) +
  scale_x_discrete("Channel") +
  xlab('Channel') +
  ylab('TRx')

```

### Visualising the multi Random Forest results EUTRx, TRx and Predicted TRx
```{r, echo = FALSE, message = FALSE, warning = FALSE, eval = TRUE}
ggplot() +
  geom_point(aes(x = test_set$EUTRx, y = test_set$TRx) , 
             color="red") +
  geom_line(aes(x= test_set$EUTRx, y = y_pred ),
            color="blue") +
 ggtitle('Truth or Bluff (Random Forest) Predicted Vs Actual') +
  scale_y_continuous("TRX", labels = scales::comma) +
  scale_x_discrete("EUTRx", labels = scales::comma) +
  xlab('EUTRx') +
  ylab('TRx')

```




